Syntax and Semantics of Abstract Binding Trees

### 2015-11-26 paper.tex
Just write out the comma constructions instead of "SCtx", "Ctx"

\newcommand\SymSets{\mathbb{I}}
\newcommand\FinSets{\mathbb{F}}
\newcommand\HypCat{\mathbf{H}}
\newcommand\Supp[1]{\mathbf{supp}(#1)}
\newcommand\SupportsUnmoded[3]{#1 \blacktriangleright_{#2} #3}
\newcommand\Supports[3]{\SupportsUnmoded{\IMode{#1}}{\IMode{#2}}{\IMode{#3}}}

@@

Let $\SymSets$ be the category of finite cardinals and their injective maps;
the the comma construction
$\Define{\SCtx}{\Comma{\SymSets}{\Discrete{\Sorts}}}$, with $\Discrete{\Sorts}$
the discrete category on the set $\Sorts$, is the category of contexts of
symbols whose objects are finite sets of symbols $U$ and sort-assignments
\begin{tikzcd}[cramped]
  \IMode{U}\arrow[r, "\IMode{\mathfrak{s}}"] &\IMode{\Sorts}
\end{tikzcd}, and whose morphisms are
sort-preserving renamings; we will write $\Upsilon$ for a symbol context
$(U,\mathfrak{s})$.

@@

\begin{remark}
  The presentation we have given above is related both to the Schanuel topos
  and, equivalently, Pitts' category of nominal sets; we differ only in
  discussing sheaves on the category of symbol contexts $\SCtx$, as opposed to
  sheaves on finite sets of symbols $\SymSets$ (i.e.\ unisorted contexts).
\end{remark}

@@

Fix a sheaf of operators
$\Of{\Operators}{\Sheaves{\OpCat{\SCtx}\times\Discrete{\Arities}}}$ such that the arrows
in $\SCtx$ lift to renamings of operators' parameters. Together, $\Sorts$ and
$\Operators$ form a \emph{signature}
$\Define{\Sigma}{\Pair{\Sorts}{\Operators}}$.

@@

Let $\FinSets$ be the free cocartesian category on a single object (that is, the
category of finite cardinals and functions between them); then the comma
construction $\Define{\Ctx}{\Comma{\FinSets}{\Sorts}}$ is the category of
variable contexts. Let $\Define{\HypCat}{\OpCat{(\SCtx\times\Ctx)}}$; then we
fix the functor category $\widehat{\HypCat}^\Sorts$ as our semantic universe.

>>>>

\newcommand\HypCat{\mathbf{H}}
\newcommand\Supp[1]{\mathbf{supp}(#1)}
\newcommand\SupportsUnmoded[3]{#1 \blacktriangleright_{#2} #3}
\newcommand\Supports[3]{\SupportsUnmoded{\IMode{#1}}{\IMode{#2}}{\IMode{#3}}}

@@

Let $\SymSets$ be the category of finite cardinals and their injective maps;
then the comma construction $\SCtx$, with $\Discrete{\Sorts}$
the discrete category on the set $\Sorts$, is the category of contexts of
symbols whose objects are finite sets of symbols $U$ and sort-assignments
\begin{tikzcd}[cramped]
  \IMode{U}\arrow[r, "\IMode{\mathfrak{s}}"] &\IMode{\Sorts}
\end{tikzcd}, and whose morphisms are
sort-preserving renamings; we will write $\Upsilon$ for a symbol context
$(U,\mathfrak{s})$.

@@

\begin{remark}
  The presentation we have given above is related both to the Schanuel topos
  and, equivalently, Pitts' category of nominal sets; we differ only in
  discussing covariant sheaves on the category of symbol contexts $\SCtx$, as
  opposed to covariant sheaves on finite sets of symbols $\SymSets$ (i.e.\
  unisorted contexts).
\end{remark}

@@

Fix a sheaf of operators
$\Of{\Operators}{\Sheaves{\OpCat{\left(\SCtx\right)}\times\Discrete{\Arities}}}$
such that the arrows in $\SCtx$ lift to renamings of operators' parameters.
Together, $\Sorts$ and $\Operators$ form a \emph{signature}
$\Define{\Sigma}{\Pair{\Sorts}{\Operators}}$.

@@

Let $\FinSets$ be category of finite cardinals and \emph{any} functions between
them; then the comma construction $\Ctx$ is the category of variable contexts.
Let $\Define{\HypCat}{\OpCat{(\SCtx\times\Ctx)}}$; then we fix the functor
category $\widehat{\HypCat}^\Sorts$ as our semantic universe.
